% Code


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(metafor)
library(broom)
library(here)
library(knitr)
library(kableExtra)
library(cowplot)
library(janitor)
```



# Meta-analysis

## Yield


```{r}
multi1 <- read_excel(here("data", "dat-yld.xlsx"), 1) 

head(multi1)
```



### Meta-analytic model

```{r}
ma1_multi_site <- rma.mv(yi2, vi2, 
                      mods = ~AI, 
                      random = list(~ AI | study, ~1 | id), 
                      struct = "UN", 
                      method = "ML", 
                      control = list(optimizer = "nlm"), 
                      data = multi1)
ma1_multi_site
```

### Contrasts

```{r}
anova(ma1_multi_site, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 1, 0, -1, 0, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 1, 0, 0, -1, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 0, 1, 0, -1, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1)))

```

### Exporting results

```{r}
yield_res<- data.frame(cbind(ma1_multi_site$b,
                             ma1_multi_site$ci.lb,
                             ma1_multi_site$ci.ub)) %>%
  mutate(fungicide = c("check", "AZOX + BENZ", "AZOX + BENZ + CLOR", "AZOX + BENZ + COPPER", "AZOX + BENZ + MANC", "PICO + CYPR", "PICO + CYPR + CLOR", "PICO + CYPR + COPPER", "PICO + CYPR + MANC","PYRA + FLUX", "PYRA + FLUX + CLOR", "PYRA + FLUX + COPPER", "PYRA + FLUX + MANC")) %>%
  filter(fungicide != "check")


names (yield_res) = c("yld", "yld_lower", "yld_upper", "fungicide")

yield_res

PICO_yld = yield_res %>%
  mutate(n = seq(1:12)) %>%
  filter(n == c(5,6,7,8)) %>%
  summarise(mean = yld - first(yld),
            lower = yld_lower - first(yld_lower),
            upper = yld_upper - first(yld_upper)) %>%
  filter(mean>0) %>%
  mutate(fungicide = rep("PICO + CYPR", length("mean"))) %>%
  mutate(multi_site = c("CLOR", "COPPER", "MANC"))

PYRA_yld = yield_res %>%
  mutate(n = seq(1:12)) %>%
  filter(n > 8) %>%
  summarise(mean = yld - first(yld),
            lower = yld_lower - first(yld_lower),
            upper = yld_upper - first(yld_upper)) %>%
  filter(mean>0) %>%
  mutate(fungicide = rep("PYRA + FLUX", length("mean"))) %>%
  mutate(multi_site = c("CLOR", "COPPER", "MANC"))

AZOX_yld = yield_res %>%
  mutate(n = seq(1:12)) %>%
  filter(n < 5) %>%
  summarise(mean = yld - first(yld),
            lower = yld_lower - first(yld_lower),
            upper = yld_upper - first(yld_upper)) %>%
  filter(mean>0) %>%
  mutate(fungicide = rep("AZOX + BENZ", length("mean"))) %>%
  mutate(multi_site = c("CLOR", "COPPER", "MANC"))

gain_yld = rbind(PICO_yld, PYRA_yld, AZOX_yld)
gain_yld

openxlsx::write.xlsx(gain_yld, here("data","gain_yld.xlsx"), colNames = TRUE)
```

### Mod: Baseline Disease 

```{r}
median(multi1$sev_check)
  
multi1 <- multi1 %>%
 mutate(baseline = case_when(
      sev_check < 80 ~ "Low",
      sev_check >= 80 ~ "High"))

multi1 %>% 
  group_by(study,baseline, AI) %>% 
  summarise() %>% 
  tabyl(AI, baseline)

multi1 %>% 
  group_by(study,baseline) %>% 
  summarise() %>% 
  tabyl(baseline)


ms_baseline <- rma.mv(yi2, vi2, 
                      mods = ~AI*as.factor(baseline), 
                      random = list(~ AI | study, ~1 | id), 
                      struct = "UN", 
                      method = "ML", 
                      control = list(optimizer = "nlm"), 
                      data = multi1)

ms_baseline

anova(ms_baseline, btt=15:26)
```

#### Mod effect

```{r}
reg1 = data.frame(ms_baseline$beta, ms_baseline$ci.lb, ms_baseline$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lado3","lixo"),sep = "[[)]]" ) %>% 
  select(-lixo) %>%
  separate(lado3, into = c("lixo","lado4"),sep = "baseline") %>%
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "AI" ) %>%
  select(-lixo) %>%
  filter(lado1 != "NA") %>% 
  set_names("fungicide", "class", "mean", "ci.lb", "ci.ub") %>%
  mutate(class = c(rep("high", 12), rep("low", 12)))
  

mean = reg1 %>% 
  group_by(fungicide) %>% 
  select(1:3) %>% 
  spread(class, mean) %>% 
  mutate(mean = (high + low)) %>% 
  select(1,4)

lower = reg1%>% 
  group_by(fungicide) %>% 
  select(1,2,4) %>% 
  spread(class, ci.lb) %>% 
  mutate(lower = (high + low)) %>% 
  select(1,4)

upper = reg1%>% 
  group_by(fungicide) %>% 
  select(1,2,5) %>% 
  spread(class, ci.ub) %>% 
  mutate(upper = (high + low)) %>% 
  select(1,4)

reg3 = left_join(mean, lower, by= c("fungicide")) %>% 
  left_join( upper, by = c("fungicide")) %>% 
  mutate(class = rep("low", length("fungicide"))) %>% 
  select("fungicide", "class", "mean", "lower", "upper")


high = reg1 %>% 
  filter(class == "high") %>% 
  set_names("fungicide", "class", "mean", "lower", "upper")


yld_baseline = rbind(high,reg3)
yld_baseline

openxlsx::write.xlsx(yld_baseline, here("data","yld_baseline_results.xlsx"), colNames = TRUE)

```


### Mod: Region 

```{r}
multi1 = multi1 %>% 
mutate(region = case_when(
    state == "MT" ~ "North",
    state == "BA" ~ "North",
    state == "MS" ~ "North",
    state == "GO" ~ "North",
    state == "PR" ~ "South",
    state == "MG" ~ "North",
    state == "SP" ~ "South",
    state == "RS" ~ "South")) 

multi1 %>%
  group_by(study,region, AI) %>% 
  summarise() %>% 
  tabyl(AI,region)

ma1_region_yld <- rma.mv(yi2, vi2, 
                      mods = ~AI * as.factor(region), 
                      random = list(~ AI | study, ~1 | id), 
                      struct = "UN", 
                      method = "ML", 
                      control = list(optimizer = "nlm"), 
                      data = multi1)
ma1_region_yld

anova(ma1_region_yld, btt=15:26)
```

### Inconsistency

We used a factorial-type ANOVA model to determine the significance of the *treatment x design* interaction, evaluated based on the Wald test statistic.

```{r}
yld_design <- read_excel(here("data", "yld_design.xlsx"), 1) 

mv_yld_design <- rma.mv(yi2, vi2, 
                      mods = ~AI * design,
                      random = list(~ 1 | study / design / AI),
                      struct = "UN", 
                      method = "ML", 
                      control = list(optimizer = "nlm"), 
                      data = yld_design)

mv_yld_design

anova(mv_yld_design,  btt=15:26)
```



## Efficacy


```{r}
multi2 <- read_excel(here("data", "dat-sev.xlsx"), 1) 

head(multi2)
```

### Meta-analytic model


```{r}
ma2_multi_site <- rma.mv(yi, vi, 
                      mods = ~AI, 
                      random = list(~ AI | study, ~1 | id), 
                      struct = "UN", 
                      method = "ML", 
                      control = list(optimizer = "nlm"), 
                      data = multi2)

ma2_multi_site

  
```

### Contrasts

```{r}


anova(ma2_multi_site, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 1, 0, -1, 0, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 1, 0, 0, -1, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 0, 1, 0, -1, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1)))


```

```{r}
efficacy = data.frame(
  estimate = round((1 - exp(ma2_multi_site$b)) * 100, 2),
  ci.lb = round((1 - exp(ma2_multi_site$ci.ub)) * 100, 2),
  ci.ub = round((1 - exp(ma2_multi_site$ci.lb)) * 100, 2)) %>%
  filter(estimate > 0) %>%
  mutate(fungicide = c( "AZOX + BENZ", "AZOX + BENZ + CLOR", "AZOX + BENZ + COPPER", "AZOX + BENZ + MANC", "PICO + CYPR", "PICO + CYPR + CLOR", "PICO + CYPR + COPPER", "PICO + CYPR + MANC","PYRA + FLUX", "PYRA + FLUX + CLOR", "PYRA + FLUX + COPPER", "PYRA + FLUX + MANC"))

names (efficacy) = c("efficacy", "eff_lower", "eff_upper", "fungicide")
efficacy
```


### Exporting results

```{r}

PICO_eff = efficacy %>%
  mutate(n = seq(1:12)) %>%
  filter(n == c(5,6,7,8)) %>%
  summarise(mean_eff = efficacy - first(efficacy),
            upper_eff = eff_lower - first(eff_lower),
            lower_eff = eff_upper - first(eff_upper)) %>%
  filter(mean_eff>0) %>%
  mutate(fungicide = rep("PICO + CYPR", length("mean_eff"))) %>%
  mutate(multi_site = c("CLOR", "COPPER", "MANC"))

PYRA_eff = efficacy %>%
  mutate(n = seq(1:12)) %>%
  filter(n > 8) %>%
  summarise(mean_eff = efficacy - first(efficacy),
            upper_eff = eff_lower - first(eff_lower),
            lower_eff = eff_upper - first(eff_upper)) %>%
  filter(mean_eff>0) %>%
  mutate(fungicide = rep("PYRA + FLUX", length("mean_eff"))) %>%
  mutate(multi_site = c("CLOR", "COPPER", "MANC"))

AZOX_eff = efficacy %>%
  mutate(n = seq(1:12)) %>%
  filter(n < 5) %>%
  summarise(mean_eff = efficacy - first(efficacy),
            upper_eff = eff_lower - first(eff_lower),
            lower_eff = eff_upper - first(eff_upper)) %>%
  filter(mean_eff>0) %>%
  mutate(fungicide = rep("AZOX + BENZ", length("mean_eff"))) %>%
  mutate(multi_site = c("CLOR", "COPPER", "MANC"))

gain_efficacy = rbind(PICO_eff, PYRA_eff, AZOX_eff)
gain_efficacy

openxlsx::write.xlsx(gain_efficacy, here("data","gain_efficacy.xlsx"), colNames = TRUE)
```


### Mod: Baseline Disease 

```{r}
median(multi2$sev_check)
  
multi2 <- multi2 %>%
 mutate(baseline = case_when(
      sev_check < 80 ~ "Low",
      sev_check >= 80 ~ "High"))

multi2 %>% 
  group_by(study,baseline, AI) %>% 
  summarise() %>% 
  tabyl(AI,baseline)

multi2 %>% 
  group_by(study,baseline) %>% 
  summarise() %>% 
  tabyl(baseline)


ms_baseline2 <- rma.mv(yi, vi, 
                      mods = ~AI*as.factor(baseline), 
                      random = list(~ AI | study, ~1 | id), 
                      struct = "UN", 
                      method = "ML", 
                      control = list(optimizer = "nlm"), 
                      data = multi2)

ms_baseline2

anova(ms_baseline2, btt=15:26)
``` 




#### Mod effect

```{r}
reg1 = data.frame(ms_baseline2$beta, ms_baseline2$ci.lb, ms_baseline2$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lado3","lixo"),sep = "[[)]]" ) %>% 
  select(-lixo) %>%
  separate(lado3, into = c("lixo","lado4"),sep = "baseline") %>%
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "AI" ) %>%
  select(-lixo) %>%
  filter(lado1 != "NA") %>% 
  set_names("fungicide", "class", "mean", "ci.lb", "ci.ub") %>%
  mutate(class = c(rep("high", 12), rep("low", 12)))
  

mean = reg1 %>% 
  group_by(fungicide) %>% 
  select(1:3) %>% 
  spread(class, mean) %>% 
  mutate(mean = (1-exp((high + low)))*100) %>% 
  select(1,4)

upper = reg1%>% 
  group_by(fungicide) %>% 
  select(1,2,4) %>% 
  spread(class, ci.lb) %>% 
  mutate(upper = (1-exp((high + low)))*100) %>% 
  select(1,4)

lower = reg1%>% 
  group_by(fungicide) %>% 
  select(1,2,5) %>% 
  spread(class, ci.ub) %>% 
  mutate(lower = (1-exp((high + low)))*100) %>% 
  select(1,4)

reg3 = left_join(mean, lower, by= c("fungicide")) %>% 
  left_join( upper, by = c("fungicide")) %>% 
  mutate(class = rep("low", length("fungicide"))) %>% 
  select("fungicide", "class", "mean", "lower", "upper")


high = reg1 %>% 
  filter(class == "high") %>% 
  group_by(fungicide, class) %>%
  summarise(mean = (1-exp(mean))*100,
            lower = (1-exp(ci.ub))*100,
            upper = (1-exp(ci.lb))*100) 

eff_baseline = rbind(high,reg3)
eff_baseline

openxlsx::write.xlsx(eff_baseline, here("data","eff_baseline_results.xlsx"), colNames = TRUE)

```

### Mod: Region 

```{r}
multi2 = multi2 %>% 
mutate(region = case_when(
    state == "MT" ~ "North",
    state == "BA" ~ "North",
    state == "MS" ~ "North",
    state == "GO" ~ "North",
    state == "PR" ~ "South",
    state == "MG" ~ "North",
    state == "SP" ~ "South",
    state == "RS" ~ "South")) 

multi2 %>%
  group_by(study,region, AI) %>% 
  summarise() %>% 
  tabyl(AI,region)

multi2 %>%
  group_by(study,region) %>% 
  summarise() %>% 
  tabyl(region)

ma2_region_sev <- rma.mv(yi, vi, 
                      mods = ~AI * as.factor(region), 
                      random = list(~ AI | study, ~1 | id), 
                      struct = "UN", 
                      method = "ML", 
                      control = list(optimizer = "nlm"), 
                      data = multi2)
ma2_region_sev

anova(ma2_region_sev, btt=15:26)
```


### Inconsistency

We used a factorial-type ANOVA model to determine the significance of the *treatment x design* interaction, evaluated based on the Wald test statistic.

```{r}
sev_design <- read_excel(here("data", "sev_design.xlsx"), 1) 

mv_sev_design <- rma.mv(yi, vi,
                      mods = ~AI * design,
                      random = list(~ 1 | study / design / AI),
                      struct = "UN", 
                      method = "ML", 
                      control = list(optimizer = "nlm"), 
                      data = sev_design)

mv_sev_design

anova(mv_sev_design,  btt=15:26)
```

