% Data

## Load packages 

```{r message=FALSE, warning=FALSE, paged.print=FALSE}

library(tidyverse)
library(here)
library(readxl)
library(metafor)
library(ggthemes)
library(cowplot)
library(knitr)
library(broom)
library(janitor)
```


## Import data

Let's first import the data from each year.



```{r}
dat_2015 <- read_excel(here("data", "multisite_2015.xlsx"), 1) %>%
  select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray) %>%
  rbind(
    (read_excel(here("data", "multisite_2015.xlsx"), 2) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 3) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 4) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 5) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 6) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 7) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 8) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 9) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 10) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 11) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 12) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 13) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 14) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 15) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 16) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 17) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2015.xlsx"), 18) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray))
  ) %>%
  mutate(YEAR = "2014/15")


```



```{r}
dat_2016 <- read_excel(here("data", "multisite_2016.xlsx"), 1) %>%
  select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray) %>%
  rbind(
    (read_excel(here("data", "multisite_2016.xlsx"), 2) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 3) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 4) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 5) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 6) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 7) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 8) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 9) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 10) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 11) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 12) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 13) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 14) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 15) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 16) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 17) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 18) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 19) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 20) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2016.xlsx"), 21) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray))
  ) %>%
  mutate(YEAR = "2015/16")
```



```{r}
dat_2017 <- read_excel(here("data", "multisite_2017.xlsx"), 1) %>%
  select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray) %>%
  rbind(
    (read_excel(here("data", "multisite_2017.xlsx"), 2) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 3) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 4) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 5) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 6) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 7) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 8) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 9) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 10) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 11) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 12) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 13) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 14) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 15) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 16) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 17) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 18) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 19) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 20) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 21) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 22) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 23) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 24) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 25) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 26) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 27) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2017.xlsx"), 28) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray))
  ) %>%
  mutate(YEAR = "2016/17")
```




```{r}
dat_2018 <- read_excel(here("data", "multisite_2018.xlsx"), 1) %>%
  select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray) %>%
  rbind(
    (read_excel(here("data", "multisite_2018.xlsx"), 2) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 3) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 4) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 5) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 6) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 7) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 8) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 9) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 10) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 11) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 12) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 13) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 14) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 15) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 16) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 17) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 18) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 19) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 20) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 21) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 22) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 23) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 24) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018.xlsx"), 25)%>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray))
    )%>%
  mutate(YEAR = "2017/18")
```



```{r}
dat_2018A <- read_excel(here("data", "multisite_2018A.xlsx"), 1) %>%
  select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray) %>%
  rbind(
    (read_excel(here("data", "multisite_2018A.xlsx"), 2) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 3) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 4) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 5) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 6) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 7) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 8) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 9) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 10) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 11) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 12) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 13) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018A.xlsx"), 14) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray))
    )%>%
  mutate(YEAR = "2017/18")
```



```{r}
dat_2018B <- read_excel(here("data", "multisite_2018B.xlsx"), 1) %>%
  select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray) %>%
  rbind(
    (read_excel(here("data", "multisite_2018B.xlsx"), 2) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018B.xlsx"), 3) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018B.xlsx"), 4) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018B.xlsx"), 5) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018B.xlsx"), 6) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018B.xlsx"), 7) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018B.xlsx"), 8) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018B.xlsx"), 9) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray)),
    (read_excel(here("data", "multisite_2018B.xlsx"), 10) %>%
      select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD,	location, state,	cultivar,	plantio, 	n_spray))
    )%>%
  mutate(YEAR = "2017/18")
```

###  Reshape

Let's gather data from each year in one unique dataset.

```{r}
dat <- rbind(dat_2015, dat_2016, dat_2017, dat_2018, dat_2018A, dat_2018B)
str(dat)
```


### Transform

#### Sev data

##### Treatment means

```{r}
sev <- dat %>%
  group_by(NOMETRAT, LOCAL, TRAT, YEAR,	location, state,	cultivar,	plantio, 	n_spray) %>%
  summarize(mean_SEV = mean(SEV)) %>%
  unite(LOCAL_YEAR, LOCAL, YEAR, sep = "_", remove = F) %>%
  ungroup() %>% 
  select(1:2, 5:8, 10, 11)
```


##### Sampling variance


```{r}

var_sev <- dat %>%
  group_by(LOCAL, YEAR) %>%
  select(NOMETRAT, REP, SEV) %>%
  group_by(LOCAL, YEAR) %>%
  do(tidy(aov(.$SEV ~ .$NOMETRAT + factor(.$REP)))) %>%
  filter(term == "Residuals") %>%
  unite(LOCAL_YEAR, LOCAL, YEAR, sep = "_", remove = F) %>%
  ungroup() %>%
  select(1,3, 7) 
```

#### Yield data

##### Treatment means

```{r}
prod <- dat %>%
  group_by(NOMETRAT, LOCAL, TRAT, YEAR,location, state,	cultivar,	plantio, 	n_spray) %>%
  summarize(mean_PROD = mean(PROD)) %>%
  unite(LOCAL_YEAR, LOCAL, YEAR, sep = "_", remove = F) %>%
  ungroup() %>%
  select(1:2, 5:8, 10, 11)
```


##### Sampling variance


```{r}

var_prod <- dat %>%
  filter(PROD != "NA") %>% 
  group_by(LOCAL, YEAR) %>%
  select(NOMETRAT, REP, PROD) %>%
  group_by(LOCAL, YEAR) %>%
  do(tidy(aov(.$PROD ~ .$NOMETRAT + factor(.$REP)))) %>%
  filter(term == "Residuals") %>%
  unite(LOCAL_YEAR, LOCAL, YEAR, sep = "_", remove = F) %>%
  ungroup() %>%
  select(1,3, 7)
```

### combine

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
caf_sev <- left_join(sev, var_sev)
caf_prod <- left_join(prod, var_prod)
caf <- caf_sev %>% bind_cols(mean_PROD = caf_prod$mean_PROD, var_prod = caf_prod$meansq) %>% 
  arrange(LOCAL_YEAR, NOMETRAT)

data.frame(table(dat_2015$NOMETRAT)) 
data.frame(table(dat_2016$NOMETRAT)) 
data.frame(table(dat_2017$NOMETRAT)) 
data.frame(table(dat_2018$NOMETRAT))
data.frame(table(dat_2018A$NOMETRAT))
data.frame(table(dat_2018B$NOMETRAT))



```

# Multi-site Analysis

```{r}
library(janitor)
caf %>% 
  tabyl(NOMETRAT, YEAR)
```


## Rename

```{r}
library(tidyverse)

mult_caf <- caf %>%
  filter(NOMETRAT == "Testemunha" |
    NOMETRAT == "Aproach & Difere" |
    NOMETRAT == "Aproach & Prevenil" |
    NOMETRAT == "Aproach & Bravonil" | 
    NOMETRAT == "Aproach & Unizeb Gold" |
    NOMETRAT == "Aproach Prima" |
    NOMETRAT == "Aproach" |
    NOMETRAT == "Aproach Prima + Difere/ Status" |
    NOMETRAT == "Aproach Prima + Previnil" |
    NOMETRAT == "Aproach Prima + Unizeb Gold" |
    NOMETRAT == "Elatus" |
    NOMETRAT == "Elatus & Bravonil" |
    NOMETRAT == "Elatus & Difere" |
    NOMETRAT == "Elatus & Prevenil" |
    NOMETRAT == "Elatus & Unizeb Gold" |
    NOMETRAT == "Elatus + Difere/ Status" |
    NOMETRAT == "Elatus + Previnil" |
    NOMETRAT == "Elatus + Unizeb Gold" |
    NOMETRAT == "Orkestra" |
    NOMETRAT == "Orkestra & Unizeb Gold" |
    NOMETRAT == "Orkestra + Difere/ Status" |
    NOMETRAT == "Orkestra + Previnil" |
    NOMETRAT == "Orkestra & Bravonil" | 
    NOMETRAT == "Orkestra + Unizeb Gold" |
    NOMETRAT == "Orkestra SC" |
    NOMETRAT == "Orkestra SC & Difere") %>% 
  filter(n_spray %in% c(3))

table(mult_caf$NOMETRAT, mult_caf$n_spray)

mult_caf$AI <- ifelse(mult_caf$NOMETRAT == "Testemunha", "AACHECK",
  ifelse(mult_caf$NOMETRAT == "Aproach Prima", "PICO + CYPR",
   ifelse(mult_caf$NOMETRAT == "Aproach & Difere", "PICO + CYPR + COPPER",   
    ifelse(mult_caf$NOMETRAT == "Aproach & Prevenil", "PICO + CYPR + CLOR",
    # ifelse(mult_caf$NOMETRAT == "Aproach & Bravonil", "PICO + CYPR + CLOR",
     ifelse(mult_caf$NOMETRAT =="Aproach & Unizeb Gold", "PICO + CYPR + MANC",
      ifelse(mult_caf$NOMETRAT == "Aproach", "PICO + CYPR",
        ifelse(mult_caf$NOMETRAT == "Elatus", "AZOX + BENZ",
         ifelse(mult_caf$NOMETRAT == "Elatus & Difere", "AZOX + BENZ + COPPER",
          ifelse(mult_caf$NOMETRAT == "Elatus & Previnil", "AZOX + BENZ + CLOR",
           ifelse(mult_caf$NOMETRAT == "Elatus & Bravonil", "AZOX + BENZ + CLOR",
            ifelse(mult_caf$NOMETRAT == "Elatus + Difere/ Status", "AZOX + BENZ + COPPER",
             ifelse(mult_caf$NOMETRAT == "Elatus + Previnil","AZOX + BENZ + CLOR",
              ifelse(mult_caf$NOMETRAT == "Elatus + Unizeb Gold","AZOX + BENZ + MANC",
               ifelse(mult_caf$NOMETRAT == "Elatus & Unizeb Gold","AZOX + BENZ + MANC",
               ifelse(mult_caf$NOMETRAT == "Orkestra","PYRA + FLUX",
                ifelse(mult_caf$NOMETRAT == "Orkestra & Unizeb Gold","PYRA + FLUX + MANC",
                 ifelse(mult_caf$NOMETRAT == "Orkestra + Difere/ Status","PYRA + FLUX + COPPER",
                  ifelse(mult_caf$NOMETRAT == "Orkestra + Previnil","PYRA + FLUX + CLOR",
                   ifelse(mult_caf$NOMETRAT == "Orkestra & Bravonil","PYRA + FLUX + CLOR",
                   ifelse(mult_caf$NOMETRAT == "Orkestra + Unizeb Gold","PYRA + FLUX + MANC",
                    ifelse(mult_caf$NOMETRAT == "Orkestra SC","PYRA + FLUX",
                     ifelse(mult_caf$NOMETRAT == "Orkestra SC & Difere","PYRA + FLUX + COPPER", 
                      ifelse(mult_caf$NOMETRAT == "Aproach Prima + Difere/ Status","PICO + CYPR + COPPER",
                       ifelse(mult_caf$NOMETRAT == "Aproach Prima + Previnil","PICO + CYPR + CLOR",
                        ifelse(mult_caf$NOMETRAT ==  "Aproach Prima + Unizeb Gold","PICO + CYPR + MANC", "NA")))))))))))))))))))))))))


mult_caf = mult_caf %>% 
  filter(AI != "NA") %>% 
  filter(YEAR != "2016/17")

table(mult_caf$YEAR)
table(mult_caf$AI,mult_caf$n_spray)

   
```

### Rename columns

```{r}
library(tidyverse)

mult_caf <- rename(mult_caf, AI = AI, fungicide = NOMETRAT, study = LOCAL_YEAR, location = location, year = YEAR, sev_r6 = mean_SEV, V_sev = meansq, yield_kg = mean_PROD, V_yield = var_prod) 

mult_caf <- mult_caf %>%
  mutate(
    year = as.factor(year),
    location = as.factor(location),
    source = "CAF"
  ) %>%
  group_by(study) %>%
  arrange(study, fungicide) %>%
  filter(length(study) > 2) %>% # remove studies with only the CHECK treatment
  ungroup() %>%
  mutate(study = as.factor(study)) 
```



### Check columns

```{r}
# these two columns will be used as moderator variables later
sbr_check = mult_caf %>% 
  ungroup() %>% 
  filter(AI == "AACHECK")  %>% 
  mutate(check = AI, sev_check = sev_r6, v_sev_check = V_sev, yld_check = yield_kg, v_yld_check = V_yield ) %>% 
  select(study, yld_check, v_yld_check, sev_check, v_sev_check)

mult_caf = mult_caf %>% 
  full_join(sbr_check)


```

## Export the file

```{r message=FALSE, warning=FALSE, paged.print=FALSE}

openxlsx::write.xlsx(mult_caf, here("data","multi_site_JPB.xlsx"), colNames = TRUE)

```


## Exploratory 


```{r}
mult_caf %>%
  tabyl(AI, n_spray)

```


```{r}
mult_caf %>%
  tabyl(AI, year)
```


```{r}
mult_caf %>%
  group_by(study,year) %>% 
  summarise() %>% 
  tabyl(year)
```


```{r}
mult_caf %>%
  group_by(study,AI) %>% 
  summarise() %>%
  tabyl(AI)

```


```{r}

mult_caf %>%
  group_by(study,location) %>% 
  summarise() %>%
  tabyl(location)

length(unique(mult_caf$location))
```



```{r}
mult_caf %>%
  group_by(study,state) %>% 
  summarise() %>% 
  tabyl(state)
```


```{r}
mult_caf %>%
  tabyl(AI, source)
```


```{r}
mult_caf %>% 
  group_by(study)
length(unique(mult_caf$study))
```

## Create datasets


### Yield 

```{r}
multi1 <- mult_caf %>%
  filter(yield_kg != "NA") %>%
  filter(yld_check != "NA") %>%
  filter(sev_check != "NA") %>%
  mutate(yi2 = yield_kg,
    vi2 = V_yield / 4) %>% 
  mutate(id = 1:nrow(.))

multi1 <- multi1 %>%
  group_by(study) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

data.frame(table(multi1$location))
data.frame(table(multi1$state))


multi1 %>% 
  group_by(study)
length(unique(multi1$study))

openxlsx::write.xlsx(multi1, here("data","dat-yld.xlsx"), colNames = TRUE)

```



#### Design groups

```{r}
multi1_designs = multi1 %>% 
  group_by(study) %>% 
  summarise(AI1 = paste(AI, collapse=';')) 

multi1_designs %>% 
  tabyl(AI1)
```

Three different designs (here design refers to the set of treatments in the trial) were found in the trials reporting soybean yield.

```{r}
design1 = multi1 %>% 
  group_by(study) %>% 
  filter(AI  %in% c("PICO + CYPR", "PICO + CYPR + COPPER", "PICO + CYPR + CLOR", "PICO + CYPR + MANC"," AZOX + BENZ", "AZOX + BENZ + CLOR", "AZOX + BENZ + COPPER", "AZOX + BENZ + MANC", "AACHECK")) %>% 
  group_by(study) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(1, length(AI))) %>% 
  filter(n3 == 8)
design1

design2 = multi1 %>% 
  group_by(study) %>% 
  filter(AI  %in% c("PICO + CYPR", "PICO + CYPR + COPPER", "PICO + CYPR + CLOR", "PICO + CYPR + MANC", "AZOX + BENZ", "AZOX + BENZ + COPPER", "AZOX + BENZ + CLOR", "AZOX + BENZ + MANC", "PYRA + FLUX + COPPER", "PYRA + FLUX + CLOR", "PYRA + FLUX + MANC", "PYRA + FLUX", "AACHECK")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(2, length(AI))) %>% 
  filter(n3 == 13)
design2

design3 = multi1 %>% 
  group_by(study) %>% 
  filter(AI  %in% c("PYRA + FLUX", "PYRA + FLUX + CLOR", "PYRA + FLUX + MANC", "PYRA + FLUX + COPPER", "AACHECK")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(3, length(AI))) %>% 
  filter(n3 == 5)
design3


yld_design = rbind(design1, design2, design3)



openxlsx::write.xlsx(yld_design, here("data","yld_design.xlsx"), colNames = TRUE)
```

### SBR Severity 

```{r}
multi2 <- mult_caf %>%
  filter(yld_check != "NA") %>%
  filter(sev_check != "NA") %>% 
  filter(sev_r6 != "NA" & sev_r6 != 0) %>% 
  slice(-420) %>% #remove a specific line by position. Remove the treatment without manc after filtering sev < 0 at the same trial
  mutate(vi = V_sev / (4* sev_r6^2),
    yi = log(sev_r6),
    id = 1:nrow(.))
multi2 <- multi2 %>%
  group_by(study) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)  

data.frame(table(multi2$location))
data.frame(table(multi2$state))



multi2 %>% 
  group_by(study)
length(unique(multi2$study))

openxlsx::write.xlsx(multi2, here("data","dat-sev.xlsx"), colNames = TRUE)

```

#### Design groups

```{r}
multi2_designs = multi2 %>% 
  group_by(study) %>% 
  summarise(AI1 = paste(AI, collapse=';')) 

multi2_designs %>% 
  tabyl(AI1)
```

Five different designs (here design refers to the set of treatments in the trial) were found in the trials reporting SBR severity.

```{r}
design1 = multi2 %>% 
  group_by(study) %>% 
  filter(AI  %in% c("PICO + CYPR", "PICO + CYPR + COPPER", "PICO + CYPR + CLOR", "PICO + CYPR + MANC"," AZOX + BENZ", "AZOX + BENZ + CLOR", "AACHECK")) %>% 
  group_by(study) %>%
  mutate(n3 = n()) %>% 
  mutate(design = rep(1, length(AI))) %>% 
  filter(n3 == 6)
design1

design2 = multi2 %>% 
  group_by(study) %>% 
  filter(AI  %in% c("PICO + CYPR", "PICO + CYPR + COPPER", "PICO + CYPR + CLOR", "PICO + CYPR + MANC"," AZOX + BENZ", "AZOX + BENZ + CLOR", "AZOX + BENZ + COPPER", "AZOX + BENZ + MANC", "AACHECK")) %>% 
  group_by(study) %>%
  mutate(n3 = n()) %>% 
  mutate(design = rep(2, length(AI))) %>% 
  filter(n3 == 8)
design2


design3 = multi2 %>% 
  group_by(study) %>% 
  filter(AI  %in% c("PICO + CYPR", "PICO + CYPR + COPPER", "PICO + CYPR + CLOR", "PICO + CYPR + MANC", "TFLX + PROT", "TFLX + PROT + COPPER", "TFLX + PROT + CLOR", "TFLX + PROT + MANC", "PYRA + FLUX + COPPER", "PYRA + FLUX + CLOR", "PYRA + FLUX + MANC", "PYRA + FLUX", "AACHECK")) %>% 
  group_by(study) %>%
  mutate(n3 = n()) %>% 
  mutate(design = rep(3, length(AI))) %>% 
  filter(n3 == 5)
design3

design4 = multi2 %>% 
  group_by(study) %>% 
  filter(AI  %in% c("PYRA + FLUX", "PYRA + FLUX + CLOR", "PYRA + FLUX + MANC", "PYRA + FLUX + COPPER", "AACHECK")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(4, length(AI))) %>% 
  filter(n3 == 5)
design4


design5 = multi2 %>% 
  group_by(study) %>% 
  filter(AI  %in% c("PYRA + FLUX", "PYRA + FLUX + MANC", "PYRA + FLUX + COPPER", "AACHECK")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(5, length(AI))) %>% 
  filter(n3 == 4)
design5


sev_design = rbind(design1, design2, design3, design4, design5)


openxlsx::write.xlsx(sev_design, here("data","sev_design.xlsx"), colNames = TRUE)
```
