% Code

## Introduction

In this analysis.. 


## Load packages

The packages necessary for this analysis..

```{r message=FALSE}
library(tidyverse)
library(readxl)
library(metafor)
library(broom)
```


## CAF data

### Import

Let's first import the data from each year.



```{r}
dat_2015 <- read_excel("multisite_2015.xlsx", 1) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD) %>% 
  rbind((read_excel("multisite_2015.xlsx", 2) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 3) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 4) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 5) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 6) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 7) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 8) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 9) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 10) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 11) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 12) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)), 
        (read_excel("multisite_2015.xlsx", 13) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 14) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 15) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 16) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 17) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 18) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD))) %>% 
  mutate(YEAR = 2015) 

dat_2015
```



```{r}
dat_2016 <- read_excel("multisite_2016.xlsx", 1) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD) %>% 
  rbind((read_excel("multisite_2016.xlsx", 2) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 3) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 4) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 5) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 6) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 7) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 8) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 9) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 10) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 11) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 12) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)), 
        (read_excel("multisite_2016.xlsx", 13) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 14) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 15) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 16) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 17) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 18) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 19) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 20) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 21) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD))) %>% 
  mutate(YEAR = 2016)

```



```{r}
dat_2017 <- read_excel("multisite_2017.xlsx", 1) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD) %>% 
  rbind((read_excel("multisite_2017.xlsx", 2) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 3) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 4) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 5) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 6) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 7) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 8) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 9) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 10) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 11) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 12) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)), 
        (read_excel("multisite_2017.xlsx", 13) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 14) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 15) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 16) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 17) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 18) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 19) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 20) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 21) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 22) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 23) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 24) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 25) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 26) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 27) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 28) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD))) %>% 
  mutate(YEAR = 2017)

```


###  Reshape

Let's gather data from each year in one unique dataset.

```{r}
dat <- rbind(dat_2015, dat_2016, dat_2017)
str(dat)


```



### Transform

#### Treatment means

```{r}
library(tidyverse)
sev <- dat %>% 
  group_by(NOMETRAT, LOCAL, TRAT, YEAR) %>% 
  summarize(mean_SEV = mean(SEV)) %>% 
  unite(LOCAL_YEAR, LOCAL, YEAR, sep = "_", remove = F) %>% 
  ungroup() %>% 
  select(1:3,5, 6)
  
```


#### Sampling variance


```{r}

var_sev <- dat %>% 
  group_by(LOCAL, YEAR) %>%  
  select(NOMETRAT, REP, SEV) %>% 
  group_by(LOCAL, YEAR) %>% 
  do(tidy(aov(.$SEV ~ .$NOMETRAT + factor(.$REP)))) %>% 
  filter(term == "Residuals") %>% 
  unite(LOCAL_YEAR, LOCAL, YEAR, sep = "_", remove = F) %>% 
  ungroup() %>% 
  select(1:3, 7)

```

### combine

```{r}
caf <- left_join(sev, var_sev)

```

### Rename 

Rename the fungicides


```{r}
library(tidyverse)
library(plyr)
caf$NOMETRAT <-  revalue(caf$NOMETRAT, c("Aproach" = "APROACH PRIMA",
                               "Aproach & Unizeb Gold" = "APROACH PRIMA+UNIZEB GOLD",
                               "Elatus" = "ELATUS",
                               "Elatus & Unizeb Gold" = "ELATUS+UNIZEB GOLD",
                               "Fox"= "FOX",
                               "Fox & Unizeb Gold 3,0" = "FOX+UNIZEB GOLD",
                               "Testemunha" = "ACHECK"
                               ))

dat_caf <- caf %>% 
  filter(NOMETRAT == "APROACH PRIMA" |
           NOMETRAT == "APROACH PRIMA+UNIZEB GOLD" |
           NOMETRAT == "ELATUS" |
           NOMETRAT == "ELATUS+UNIZEB GOLD"|
           NOMETRAT == "FOX" |
           NOMETRAT == "FOX+UNIZEB GOLD" |
         NOMETRAT == "ACHECK")



```

Rename the colums

```{r}
detach("package:plyr", unload=TRUE)
library(tidyverse)

dat_caf <- rename(dat_caf, fungicide = NOMETRAT, study = LOCAL_YEAR ,  location = LOCAL , year = YEAR, sev_r6 = mean_SEV, V_sev = meansq)

dat_caf <- dat_caf %>% 
  mutate(study = as.factor(study),
         source = "CAF")

```


## UPL data

```{r}
dat_upl <- read_excel("dat_upl.xlsx") %>% 
  select(fungicide, study, location, year, sev_r6, V_sev) %>% 
  filter(fungicide != "APROACH PRIMA+MANFIL" &
           fungicide != "ELATUS+MANFIL" )
          


dat_upl <- dat_upl %>% 
  mutate(study = as.factor(study),
         source = "UPL")
library(plyr)
dat_upl$fungicide <-  revalue(dat_upl$fungicide, c("CHECK" = "ACHECK"
                               ))

```



## Combine CAF and UPL

```{r}

caf_upl <- rbind(dat_upl, dat_caf)

```

## Exploratory 


```{r}
caf_upl %>% 
  ggplot(aes(fungicide, sev_r6))+
  geom_boxplot()+
  facet_wrap(~ source)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


## Meta-analysis

### Effect-size and variance

We will use the log of means and respective sampling variance


```{r}
caf_upl2 <- caf_upl %>% 
  mutate(vi = V_sev / (4 * sev_r6^2),
         yi = log(sev_r6)) %>% 
  filter (yi != "NA", 
          vi < 8)

```

### Multivariate meta-analysis

#### Overal effect 

```{r,cache=TRUE}

ma1_caf_upl <- rma.mv(yi, vi, mods= ~fungicide, random = list(~ fungicide | study), struct="UN", method="ML",  control = list(optimizer="nlm"), data = caf_upl2)

```



```{r}

summary(ma1_caf_upl)

anova(ma1_caf_upl, L=rbind(c(0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0),
                         c(0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0),
                         c(0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0),
                         c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0),
                         c(0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0),
                         c(0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0),
                         c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1)))

data.frame(estimate = round((1-exp(ma1_caf_upl$b))*100, 4), 
           ci.lb = round((1-exp(ma1_caf_upl$ci.ub))*100, 4),
           ci.ub = round((1-exp(ma1_caf_upl$ci.lb))*100, 4))


# number of trials by fungicide
library(knitr)
dat_freq <- data.frame(table(AI = caf_upl2$fungicide, caf_upl2$study))
dat_freq2 <- dat_freq %>% 
  filter(Freq > 0)
kable(data.frame(table(AI = dat_freq2$AI)))


data.frame(table(AI = caf_upl2$fungicide))
```

#### Effect of data source

```{r,cache=TRUE}
ma2_caf_upl <- rma.mv(yi, vi, mods= ~fungicide*source, random = list(~ fungicide | study), method="ML", struct="UN", control = list(optimizer="nlm"), data = caf_upl2)
```

```{r}
summary(ma2_caf_upl)

data.frame(estimate = round((1-exp(ma2_caf_upl$b))*100, 4), 
           ci.lb = round((1-exp(ma2_caf_upl$ci.ub))*100, 4),
           ci.ub = round((1-exp(ma2_caf_upl$ci.lb))*100, 4))



anova(ma2_caf_upl,btt=9:14)

```
```





