% Code

## Introduction

In this analysis.. 


## Load packages

The packages necessary for this analysis..

```{r message=FALSE}
library(tidyverse)
library(readxl)
library(metafor)
library(broom)
```


## CAF data

### Import

Let's first import the data from each year.



```{r}
dat_2015 <- read_excel("multisite_2015.xlsx", 1) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD) %>% 
  rbind((read_excel("multisite_2015.xlsx", 2) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 3) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 4) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 5) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 6) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 7) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 8) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 9) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 10) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 11) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 12) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)), 
        (read_excel("multisite_2015.xlsx", 13) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 14) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 15) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 16) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 17) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2015.xlsx", 18) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD))) %>% 
  mutate(YEAR = 2015) 

dat_2015
```



```{r}
dat_2016 <- read_excel("multisite_2016.xlsx", 1) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD) %>% 
  rbind((read_excel("multisite_2016.xlsx", 2) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 3) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 4) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 5) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 6) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 7) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 8) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 9) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 10) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 11) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 12) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)), 
        (read_excel("multisite_2016.xlsx", 13) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 14) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 15) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 16) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 17) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 18) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 19) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 20) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2016.xlsx", 21) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD))) %>% 
  mutate(YEAR = 2016)

```



```{r}
dat_2017 <- read_excel("multisite_2017.xlsx", 1) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD) %>% 
  rbind((read_excel("multisite_2017.xlsx", 2) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 3) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 4) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 5) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 6) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 7) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 8) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 9) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 10) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 11) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 12) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)), 
        (read_excel("multisite_2017.xlsx", 13) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 14) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 15) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 16) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 17) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 18) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 19) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 20) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 21) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 22) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 23) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 24) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 25) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 26) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 27) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD)),
        (read_excel("multisite_2017.xlsx", 28) %>% select(NOMETRAT, LOCAL, TRAT, REP, SEV, PROD))) %>% 
  mutate(YEAR = 2017)

```


###  Reshape

Let's gather data from each year in one unique dataset.

```{r}
dat <- rbind(dat_2015, dat_2016, dat_2017)
str(dat)


```



### Transform

#### Treatment means

```{r}
library(tidyverse)
prod <- dat %>% 
  group_by(NOMETRAT, LOCAL, TRAT, YEAR) %>% 
  summarize(mean_PROD = mean(PROD)) %>% 
  unite(LOCAL_YEAR, LOCAL, YEAR, sep = "_", remove = F) %>% 
  ungroup() %>% 
  select(1:3,5, 6)
  
```


#### Sampling variance


```{r}

var_prod <- dat %>% 
  group_by(LOCAL, YEAR) %>%  
  select(NOMETRAT, REP, PROD) %>% 
  group_by(LOCAL, YEAR) %>% 
  do(tidy(aov(.$PROD ~ .$NOMETRAT + factor(.$REP)))) %>% 
  filter(term == "Residuals") %>% 
  unite(LOCAL_YEAR, LOCAL, YEAR, sep = "_", remove = F) %>% 
  ungroup() %>% 
  select(1:3, 7)

```

### combine

```{r}
caf <- left_join(prod, var_prod)

```

### Rename 

Rename the fungicides


```{r}
library(tidyverse)
library(plyr)
caf$NOMETRAT <-  revalue(caf$NOMETRAT, c("Aproach" = "APROACH PRIMA",
                               "Aproach & Unizeb Gold" = "APROACH PRIMA+UNIZEB GOLD",
                               "Elatus" = "ELATUS",
                               "Elatus & Unizeb Gold" = "ELATUS+UNIZEB GOLD",
                               "Fox"= "FOX",
                               "Fox & Unizeb Gold 3,0" = "FOX+UNIZEB GOLD",
                               "Testemunha" = "ACHECK"
                               ))

dat_caf <- caf %>% 
  filter(NOMETRAT == "APROACH PRIMA" |
           NOMETRAT == "APROACH PRIMA+UNIZEB GOLD" |
           NOMETRAT == "ELATUS" |
           NOMETRAT == "ELATUS+UNIZEB GOLD"|
           NOMETRAT == "FOX" |
           NOMETRAT == "FOX+UNIZEB GOLD" |
         NOMETRAT == "ACHECK")



```

### Rename the colums

```{r}
detach("package:plyr", unload=TRUE)
library(tidyverse)

dat_caf <- rename(dat_caf, fungicide = NOMETRAT, study = LOCAL_YEAR ,  location = LOCAL , year = YEAR, yield_kg = mean_PROD, V_yield = meansq)

dat_caf <- dat_caf %>% 
  mutate(study = as.factor(study),
         source = "CAF") %>% 
  filter(length(study)>1) 


dat_caf1 <- dat_caf %>% group_by(study) %>% 
  arrange (study, fungicide)

```
# Descritive analysis

## number of studies by fungicide

```{r}
library(knitr)
dat_freq <- data.frame(table(fungicide = dat_caf$fungicide, dat_caf$study))
dat_freq2 <- dat_freq %>% 
  filter(Freq > 0)
kable(data.frame(table(dat_freq2$fungicide)))

data.frame(table(dat_caf$fungicide))
```



## UPL data

```{r}
dat_upl <- read_excel("dat_upl.xlsx", 2) %>% 
  select(fungicide, study, location, year, yield_kg, V_yield) %>% 
  filter(fungicide != "APROACH PRIMA+MANFIL" &
           fungicide != "ELATUS+MANFIL" )
          
#data.frame(table(dat_upl$fungicide))

dat_upl <- dat_upl %>% 
  mutate(study = as.factor(study),
         source = "UPL")
library(plyr)
dat_upl$fungicide <-  revalue(dat_upl$fungicide, c("CHECK" = "ACHECK"
                               ))

```



## Combine CAF and UPL

```{r}

caf_upl <- rbind(dat_upl, dat_caf)

```

## Exploratory 


```{r}
caf_upl %>% 
  ggplot(aes(fungicide, yield_kg))+
  geom_boxplot()+
  facet_wrap(~ source)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


## Meta-analysis

### Effect-size and variance

We will use the log of means and respective sampling variance


```{r}
caf_upl2 <- caf_upl %>% 
  mutate(vi = V_yield / (4 * yield_kg^2),
         yi = log(yield_kg),
         yi2 = yield_kg,
         vi2 = V_yield/4,
         id <- 1:nrow(.)) %>% 
  filter (yi != "NA")

```

### Multivariate meta-analysis

#### Overal effect 

```{r,cache=TRUE}

ma1_caf_upl <- rma.mv(yi2, vi2, mods= ~fungicide, random = list(~ fungicide | study), struct="UN", method="ML",  control = list(optimizer="nlm"), data = caf_upl2)

```



```{r}

summary(ma1_caf_upl)

anova(ma1_caf_upl, L=rbind(c(0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0),
                         c(0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0),
                         c(0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0),
                         c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0),
                         c(0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0),
                         c(0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0),
                         c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1)))


```

#### Effect of data source

```{r,cache=TRUE}
ma2_caf_upl <- rma.mv(yi2, vi2, mods= ~fungicide*source, random = list(~ fungicide | study), method="ML", struct="UN", control = list(optimizer="nlm"), data = caf_upl2)
```

```{r}
summary(ma2_caf_upl)

anova(ma2_caf_upl,btt=16:21)

```
```





