---
title: Yield return of DMI+QoI mixtures plus mancozeb on Asian soybean rust 
author: "Franklin Machado"
date: "September 5, 2017"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, echo = FALSE)

# Load packages 
library(tidyverse)
library(plyr)
library(readxl)
library(metafor)
library(ggthemes)
library(cowplot)
library(scales)
library(knitr)
library(nloptr)
library(minqa)
library(broom)
library(DT)
```


# Import data

```{r}
dat_filtrado <- read_excel("dat_filtrado.xlsx", 2) %>% filter(yield_kg != "NA")

kable(dat_filtrado %>% filter(AI == "AACHECK") %>% mutate(local = paste(location, state, sep =  ", ")) %>% select(study, year, local, cultivar, check_sev_r6, check_yield_kg))


dat_filtrado %>% filter(AI == "AACHECK") %>% summary(.$check_yield_kg)

```

# Descritive

## Entries by active ingridients

```{r}

kable(data.frame(table(dat_filtrado$AI)))
length(unique(dat_filtrado$study))

```

## Studies by active ingridients

```{r}
dat6 <- data.frame(table(dat_filtrado$AI, dat_filtrado$study))
dat7 <- dat6 %>% 
  filter(Freq > 0)
kable(data.frame(table(dat7$Var1)))

```

# Meta-analysis

## D

```{r}


ma_AI_filtrado <- rma.mv(yi2, vi2, mods= ~ AI,  method="ML", random = list(~ AI | study, ~1 | id), struct="UN", control = list(optimizer="nlm"), data=dat_filtrado)

summary(ma_AI_filtrado)

anova(ma_AI_filtrado, L=rbind(c(0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0),
                     c(0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0),
                     c(0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0),
                     c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0),
                     c(0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0),
                     c(0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0),
                     c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1)))


```

## Percent yield return

```{r}
ma_AI_perc_yield2 <- rma.mv(yi, vi, mods= ~ AI,  method="ML", random = list(~ AI | study, ~1 | id),  struct="UN",control = list(optimizer="nlm"), data=dat_filtrado)

summary(ma_AI_perc_yield2)

anova(ma_AI_perc_yield2, L=rbind(c(0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0),
                         c(0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0),
                         c(0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0),
                         c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0),
                         c(0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0),
                         c(0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0),
                         c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1)))

data.frame(estimate = round((exp(ma_AI_perc_yield2$b)-1)*100, 4), 
           ci.lb = round((exp(ma_AI_perc_yield2$ci.lb)-1)*100, 4),
           ci.ub = round((exp(ma_AI_perc_yield2$ci.ub)-1)*100, 4))
```


## Effect of the number of applications on yield return (D) by AI

### Descritive 

#### Number of studies by active ingridients

```{r}
dat6 <- data.frame(table(AI = dat_filtrado$AI, n_spray = dat_filtrado$n_spray))
dat6 %>% group_by(n_spray) %>% 
  filter(Freq > 0)

```

### M-A

```{r}

ma_AI_nspray <- rma.mv(yi2, vi2, mods= ~ AI * factor(n_spray),  method="ML", random = list(~ AI | study, ~1 | id), struct="UN", control = list(optimizer="nlm"), data=dat_filtrado)

summary(ma_AI_nspray)

```

## Effect of the disease pressure on yield return (D) by AI

### Descritive 

#### Entries by active ingridients

```{r}
# Create a variable dis_press (low = <60%; high = >=60%)
dat_filtrado$dis_press <- ifelse(dat_filtrado$check_sev_r6 < 60, "low", "high")

dat6 <- data.frame(table(AI = dat_filtrado$AI, dis_press = dat_filtrado$dis_press))
dat6 %>% group_by(dis_press) %>% 
  filter(Freq > 0)

```

### M-A

```{r}

ma_AI_nspray <- rma.mv(yi2, vi2, mods= ~ AI * dis_press,  method="ML", random = list(~ AI | study, ~1 | id), struct="UN", control = list(optimizer="nlm"), data=dat_filtrado)

summary(ma_AI_nspray)

```

# Plots

## Boxplot yield by fungicide

```{r}

dat_filtrado %>% filter(yield_kg != "NA") %>% ggplot(aes(AI, yield_kg, fill = manc))+
geom_boxplot(outlier.size = NA)+ 
  theme_minimal()+
geom_jitter(width = 0.1, height = 0.1, shape = 21, alpha=0.4)+
theme(axis.text.x = element_text(angle = 25, hjust = 1))+
scale_fill_grey(start = 0.5, end = 0.95)+
  scale_x_discrete(labels = c("AACHECK" = "CHECK"))+
  theme(legend.position = "none")+
  labs(title ="", x = "", y = "Yield (kg/ha)")+
  ggsave("figs/yield_AI.png", width=7, height=4)

```

## Other option Boxplot yield by fungicide

### create variable for each fungicide

```{r}
dat_filtrado$fung_name <- ifelse(dat_filtrado$AI == "PICO + CYPR", "PICO + CYPR",
                          ifelse(dat_filtrado$AI == "PICO + CYPR + MANC","PICO + CYPR",
                          ifelse(dat_filtrado$AI == "AZOX + BENZ","AZOX + BENZ",
                          ifelse(dat_filtrado$AI == "AZOX + BENZ + MANC","AZOX + BENZ",
                          ifelse(dat_filtrado$AI == "TFLX + PROT", "TFLX + PROT",
                          ifelse(dat_filtrado$AI == "TFLX + PROT + MANC","TFLX + PROT",
                          ifelse(dat_filtrado$AI == "PICO + TEBU","PICO + TEBU",
                          ifelse(dat_filtrado$AI == "PICO + TEBU + MANC","PICO + TEBU",
                          ifelse(dat_filtrado$AI == "PYRA + EPOX","PYRA + EPOX",
                          ifelse(dat_filtrado$AI == "PYRA + EPOX + MANC","PYRA + EPOX",
                          ifelse(dat_filtrado$AI == "PYRA + FLUX", "PYRA + FLUX",
                          ifelse(dat_filtrado$AI == "PYRA + FLUX + MANC", "PYRA + FLUX",
                          ifelse(dat_filtrado$AI == "AZOX + CYPR","AZOX + CYPR",
                          ifelse(dat_filtrado$AI == "AZOX + CYPR + MANC","AZOX + CYPR","AACHECK"))))))))))))))

```

### Plot 

```{r}

yield_AI_box <- dat_filtrado %>% filter(yield_kg != "NA") %>% 
  ggplot(aes(fung_name, yield_kg,  fill = manc))+
  geom_boxplot(outlier.colour = NA, position = position_dodge(width = 0.9))+ 
  theme_minimal()+
  geom_jitter(position=position_jitterdodge(dodge.width=0.95),  shape = 21, size=1,  alpha=0.7)+
  #theme(axis.text.x = element_text(angle = 25, hjust = 1))+
  scale_x_discrete(labels = c("AACHECK" = "CHECK"))+
  scale_fill_grey(start = 0.3, end = 0.95)+
   scale_x_discrete(labels = c("AACHECK" = "CHECK", "AZOX + BENZ" = "AZOX \n +\n BENZ", "AZOX + CYPR" = "AZOX \n +\n CYPR","PICO + CYPR" = "PICO \n +\n CYPR", "PICO + TEBU" = "PICO \n +\n TEBU", "PYRA + EPOX" = "PYRA \n +\n EPOX", "PYRA + FLUX" = "PYRA \n +\n FLUX", "TFLX + PROT" = "TFLX \n +\n PROT"))+
 theme(legend.position = "none" 
        #axis.text.x=element_blank(),
       #legend.margin = margin(-1, 0, 0, 0)
       )+
  labs(title ="", x = "", y = "Yield (kg/ha)", fill = "")+
  scale_y_continuous(breaks=c(0, 1000,  2000, 3000, 4000, 5000, 6000))


```
